Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-09 paper.Rmd
Updated header info

---
title: "Assessing the Global COVID19 Impact on Air Transport with Open Data"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  bookdown::pdf_book:
     base_format: rticles::ieee_article
bibliography: "DASC2021.bib"
affiliation:
  ## use one only of the following
  # author-columnar: true         ## one column per author
  institution-columnar: true  ## one column per institution  
  # wide: true          ## one column wide author/affiliation fields
  institution:
    - name: EUROCONTROL
      department: Performance Review Unit
      location: Brussels (Belgium)
      #mark: 1
      author:
        - name: Rainer Koelle
          email: rainer.koelle@eurocontrol.int
    - name: DECEA
      department: tbd ... 
      location: tbd location - suggest Rio (Brazil)
      #mark: 2
      author:
        - name: Fabio Coneiro Barbarosa
          email: second_author@somedomain.com
abstract: |
  This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global     connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a “greener” manner. The project builds on openly available data sets. The paper will be produced in a reproducible manner making the data, code, and its processing available to interested reseachers and practitioners. The open assessment will provide policy makers with a tool to assess the reaction to local or regional measures.
  <!-- motivation -->
  <!-- short background - why important -->
  <!-- approach chosen / research method -->
  <!-- experimental work -->
  <!-- results obtained -->
  <!-- conclusions / key take-away --> 
---

>>>>

---
title: "Assessing the Global COVID19 Impact on Air Transport with Open Data"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  bookdown::pdf_book:
     base_format: rticles::ieee_article
bibliography: "DASC2021.bib"
affiliation:
  ## use one only of the following
  # author-columnar: true         ## one column per author
  institution-columnar: true  ## one column per institution  
  # wide: true          ## one column wide author/affiliation fields
  institution:
    - name: EUROCONTROL
      department: Performance Review Unit
      location: Brussels (Belgium)
      #mark: 1
      author:
        - name: Rainer Koelle
          email: rainer.koelle@eurocontrol.int
    - name: DECEA
      department: Subdepartment of Operations 
      location: Rio de Janeiro (Brazil)
      #mark: 2
      author:
        - name: Fabio Lourenco Carneiro Barbosa
          email: barbosaflcb@fab.mil.br
abstract: |
  This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global     connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a “greener” manner. The project builds on openly available data sets. The paper will be produced in a reproducible manner making the data, code, and its processing available to interested reseachers and practitioners. The open assessment will provide policy makers with a tool to assess the reaction to local or regional measures.
  <!-- motivation -->
  <!-- short background - why important -->
  <!-- approach chosen / research method -->
  <!-- experimental work -->
  <!-- results obtained -->
  <!-- conclusions / key take-away --> 
---
